\documentclass[onecard,frame]{flashcards}

\cardfrontstyle[\large\slshape]{headings}
\cardbackstyle{empty}
\cardfrontfoot{Category Theory}

%\usepackage{amsfonts}
\usepackage{amssymb,amsmath,tikz-cd}
\usepackage[T1]{fontenc}

\begin{document}

\input{tex.macros}

\long\def\Comdiag#1{
\begin{center}
\begin{tikzcd}[ampersand replacement=\&]
#1
\end{tikzcd}
\end{center}
}

\Card{Intro}{Author, copyleft}{Ben Klemens, CC BY/SA/NC}

\Dcard{Domain of $f$}{ For $f:X\to Y$, $X$.}
\Dcard{Codomain of $f$}{ For $f:X\to Y$, $Y$.}

\Dcard{Composition of $f$ and $g$}{
As a diagram,
\Comdiag{
X \arrow[r,"f"] \&Y \arrow[r, "g"] \& Z
}

Written $g \circ f: X\to Z$.
}

\Dcard{$Hom_{\bf \rm set}(X,Y)$}{The set of functions $X\to Y$}

\Dcard{Equality of $f$ and $g$}{
$f:X\to Y$ and $g:X\to Y$
are equal iff $f(x)=g(x), \forall x \in X$
}

\Dcard{Identity function on $X$}{
${\rm id}_X:X\to X$ such that ${\rm id}_X(x) = x, \forall x\in X$.
}

\Dcard{Isomorpism}{
A one-to-one correspondence.

\Comdiag{
    X \arrow[r,"\cong"] \&Y
}
There exists a function $g:Y\to X$ such that
$g \circ f = {\rm id}_X$ and
$f \circ g = {\rm id}_Y$.
}

\Card{Characteristics}{Properties of an isomorphism}{
\items{
\item Reflexive: Any set is isomorphic to itself.
\item Commutative: if $f:A\to B$ has inverse $g:B\to A$, then $g$ has inverse $f$.
\item Transitive: $A$ isomorphic to $B$ and $B$ isomorphic to $C$ $\Rightarrow$ $A$ is
isomorphic to $C$.
}
}

\Card{Notation}{$\underline n$}{The set $\{1, 2,\dots n\}$}

\Dcard{Cardinality of finite set $X$}{$|X| = n$ iff

\Comdiag{
    X \arrow[r,"\cong"] \&\underline n
}
}

\Card{Lemma}{Cardinality of $A$ and $B$  given \begin{tikzcd}[ampersand replacement=\&]
    A \arrow[r,"\cong"] \&B
\end{tikzcd}
}{|A| = |B|}

\Dcard{Injective}{
    For $F:A\to B$, $f(x) = f(y)$ only if $x=y$: points map to different values.}


\Dcard{A diagram commutes}{
    All paths from top left to bottom right are equal. E.g.,
    \Comdiag{
    A \ar[r, "f"] \ar[dr,"h"'] \& B\ar[d, "g"]\\
            \& C
    }
    commutes iff $g\circ f = h$.
}

\Dcard{Product of two sets}{
    The set of ordered pairs. For sets $X$ and $Y$,
    $${(x,y)|x\in X, y\in Y}.$$
}

\Dcard{Projection function $\pi_i$}{
    Given a product $X\times Y$ with elements $(x, y)$, $\pi_1: X\times Y \to X$ produces
    $x$. Similarly for $\pi_2$.

    \Comdiag{
        \& X \times Y \ar[dl,"\pi_1"'] \ar[dr,"\pi_2"]\\
        X \&  \& Y 
    }
}

\Dcard{Universal property of projections}{
    For any set A and any $f:A\to X$ and $g:A\to Y$, $\exists$ a unique $f\times g$ so this commutes:
    \Comdiag{
        \& X\times Y \ar[dl,"\pi_1"'] \ar[dr,"\pi_2"] \\
    X \& \& Y \\
    \& A \ar[ul, "\forall f"] \ar[ur, "\forall g"'] \ar[uu, dashrightarrow, "f\times g"]
    }

}

\Card{Notation}{$X\sqcup Y$}{
    The union of the elements of $X$ and $Y$, via indicator functions $i_1: X\to X\sqcup Y$ and $i_2$:

    \Comdiag{
        X \ar[dr,"i_1"'] \& \& Y \ar[dl,"i_2"] \\
        \& X\sqcup Y
    }
    Elements of $X\sqcup Y$ have a source indicator, so if $z\in X$ and $z\in Y$,
    $i_1z, i_2z \in X\sqcup Y$.
}

\Dcard{Universal property of coproducts}{
    For any $f:X\to A$, $g:Y\to A$, $\exists$ a unique $f\sqcup g:X\sqcup Y\to A$:
    \Comdiag{
        \& A \\
        X \ar[dr,"i_1"'] \ar[ur,"\forall f"] \& \& Y \ar[dl,"i_2"] \ar[ul,"\forall g"']\\
        \& X\sqcup Y \ar[uu, dashrightarrow, "f\sqcup g"]
    }
}

\Dcard{Fiber product}{
    Given \Comdiag{
        \& Y \ar[d,"g"]\\
        X \ar[r, "f"] \& Z
    }
    $X \times_Z Y \equiv \{(x,w,y)| f(x)=w=g(y)\}$.
}

\Dcard{Pullback}{
    Any set $W$ isomorphic to the fiber product $X\times_Z Y$, giving the commutative diagram
    \Comdiag{
        W \ar[r, "\pi_2"] \ar[d, "\pi_1"'] \& Y \ar[d,"g"]\\
        X \ar[r, "f"] \& Z
    }
}

\Dcard{Universal property for pullbacks}{
    Given $t:X\to Z$ and $u:Y\to Z$,
    $\exists$ a unique function $f\times_Z g: A\to X\times_z Y$ such that
    \Comdiag{
        X\times_Z Y \arrow[drr, bend left, "\pi_1"] \arrow[ddr, bend right, "\pi_2"] \& \& \\
        \& A\arrow[ul, dotted, "f\times_Z g" description] \arrow[r, "\forall f"] \arrow[d, "\forall g"]
        \& Y \arrow[d, "u"] \\
        \& X \arrow[r, "t"] \& Z
    }
}




\Dcard{Epimorphism}{
    $F$ is {\em epic} or an {\em epi} iff $g_1 f = g_2 f \Rightarrow g_1 = g_2$.

    \Comdiag{
    X \arrow[r,"f"] \&Y \arrow[r, shift left,"g_1"] \arrow[r,"g_2"'] \& Z
    }

    Analogous to an injective function.
}

\Card{Definition}{Monorphism}{
    $F$ is {\em monic} or {\em mono} iff $f g_1 = f g_2 \Rightarrow g_1 = g_2$.

    \Comdiag{
    Z \arrow[r, shift left,"g_1"] \arrow[r,"g_2"'] \&Y \arrow[r,"f"] \& X
    }

}

\Card{Definition}{Isomorphism}{
    A mapping that is epic and monic.
}

\Card{Definition}{Group}{
A set with a binary operation that is

\items{
\item    closed
\item    associative,
\item    has an identity, and
\item    has an inverse
}
}

\Dcard{Closed mapping}{For any element $x\in S$, $f(x)\in S$.}

\Dcard{Associative mapping}{A mapping $f:S\times S$ is
associative iff $f(s_1, f(s_2, s_3)) = f(f(s_1, s_2), s_3)$.
}

\Dcard{Magma}{A set with a closed mapping.}

\Dcard{Semigroup}{A set with a closed, associative mapping.

A magma whose operation is also associative.}

\Dcard{Hom set of $A$, $B$}{The set of mappings between $A$ and $B$}

\end{document}
